---
title: "Mini-Project 2"
author: "Your Name Here"
date: "October 31, 2017"
output: html_document
---


## Loading the data

Hypothosis:
We believe that after the Supreme Cout decision that allowed corporations to contribute to political campaigns, there was a substantial increase in committee spending, most expecially in the swing states of:
In the West, they are: Colorado, Nevada and New Mexico.
In the Midwest: Wisconsin and Ohio.
In the South: Virginia, North Carolina and Florida.
And in the Northeast: Pennsylvania and New Hampshire.

```{r, include=FALSE}
load("house_elections.rda")
load("candidates.rda")
load("committees.rda")
load("contributions.rda")
```


```{r}
library(tidyverse)
candidate_contribution_2 <- merge.data.frame(candidates, contributions, by = "cand_id", all = TRUE)

Candidate_contribution_tidy_2 <- candidate_contribution_2 %>% filter(candidates %in% c("CO", "NV", "NM", "WI", "OH", "VA", "NC", "FL", "PA", "NH")) %>% filter(contributions %in% c("CO", "NV", "NM", "WI", "OH", "VA", "NC", "FL", "PA", "NH")) 

```

